Spoken Corpus of Karel Mako\v{n}

### 2018-04-14 2018-clarin-pisa/makon-data.tex
clarin2018: polishing

The mystical, religious and spiritual nature of Mako\v{n}'s talks put K.M. in
direct antagonism with the communist regime. The opposition was strictly
unidirectional though, as Mako\v{n}
was far from wasting his energy on a fight against it. His way of dealing
with the conflict was by staying out of wide popularity. Hence, most of the
talks have been given during regular meetings in various places of
Czechoslovakia and later the Czech Republic, in a close circle of friends.

@@

The community managed to provide over 66 hours of high-quality manual
transcriptions, which have been used gradually as training data. Now, the
acoustically intact recordings are automatically transcribed well enough to
allow reading along and to do full-text search.

@@

\begin{table}[htpb]
\begin{center}
\begin{tabular}{|l|l|r|r|r|r|}
\hline
Term &
Query &
\makecell{hits in automatic\\
transcription} &
\makecell{expected hits\\
in automatic\\
transcription} &
\makecell{hits in manual\\
transcription} &
Precision \\
\hline
Lazarus & \texttt{lazar.*} & 16 & 171 & 14 & 8/10   \\
Mithra & \texttt{mithra.*|mitra.*} & 0 & 0 & 0 & n/a   \\
Satan & \texttt{satan.*} & 308 & 1575 & 129 & 16/20   \\
St. Teresa & \texttt{terez.*} & 882 & 1111 & 91 & 15/20   \\
fairy-tale & \texttt{pohádk.*} & 216 & 671 & 55 & 18/20   \\
\hline
\multicolumn{5}{|l|}{average precision} & 81.25\%\\
\hline
\end{tabular}
\caption{Text search hits in the transcription; precision only calculated from
automatic transcription}\label{tab:topicsearch}
\end{center}
\end{table}

@@

7.6\% of the total words in the corpus are manually transcribed.

@@

K.M. was writing, translating and commenting books most of his life. We can
assume that the book he was just working on influenced the topic of his talks. 
For on, he translated the book \emph{El Castillo Interior}, English \emph{The
Interior Castle} by St. Teresa of Ávila in 1988. For most recordings, the year
of their acquisition is known.  Figure~\ref{fig:teresa-year} shows how many hits
for the name of the Saint are present in the transcription by recording year.

>>>>

The mystical, religious and spiritual nature of his talks put K.M. in
direct antagonism with the communist regime. The opposition was strictly
unidirectional though, as Mako\v{n}
was far from wasting his energy on a fight against it. His way of dealing
with the conflict was by staying out of wide popularity. Hence, most of the
talks have been given during regular meetings in various places of
Czechoslovakia and later the Czech Republic, in a narrow circle of friends.

@@

The community managed to provide over 66 hours of high-quality manual
transcriptions through the web application and which have been used gradually
as training data. Now, the acoustically intact recordings are automatically
transcribed well enough to allow reading along and to do full-text search.

@@

\begin{table}[htpb]
\begin{center}
\begin{tabular}{|l|l|r|r|r|r|}
\hline
Term &
Query &
\makecell{hits in automatic\\
transcription} &
\makecell{expected hits\\
in automatic\\
transcription} &
\makecell{hits in manual\\
transcription} &
Precision \\
\hline
Lazarus & \texttt{lazar.*} & 16 & 171 & 14 & 8/10   \\
Mithra & \texttt{mithra.*|mitra.*} & 0 & 0 & 0 & n/a   \\
Satan & \texttt{satan.*} & 308 & 1575 & 129 & 16/20   \\
St. Teresa & \texttt{terez.*} & 882 & 1111 & 91 & 15/20   \\
fairy-tale & \texttt{pohádk.*} & 216 & 671 & 55 & 18/20   \\
\hline
\multicolumn{5}{|l|}{average precision} & 81.25\%\\
\hline
\end{tabular}
\caption{Text search hits in the transcription; precision only calculated from
automatic part}\label{tab:topicsearch}
\end{center}
\end{table}

@@

7.6\% of the total words in the corpus are manually transcribed. The column
``expected hits'' interpolates how many occurrences should appear given equal
frequency. Oddly enough, the ratio of the expected and actual hits varies a lot
among the search terms. It is almost certain that at least for some of them, the
recall is very low.

@@

K.M. was writing, translating and commenting books most of his life. We can
assume that the book he was just working on influenced the topic of his talks. 
For one, he translated the book \emph{El Castillo Interior}, English \emph{The
Interior Castle} by St. Teresa of Ávila in 1988. For most recordings, the year
of their acquisition is known.  Figure~\ref{fig:teresa-year} shows how many hits
for the name of the Saint are present in the transcription by recording year.
